The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-09-03 borel-regularity.tex
Add context for thimble integral results

Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.
\begin{theorem}[also \ref{thm:maxim-proof}]\label{thm:maxim}
If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly:
\begin{enumerate}
\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$. Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
\item\label{part-2} The Borel transform $\series{\iota}_a \defeq \borel_\zeta \series{I}_a$ converges near $\zeta = \alpha$.
\item\label{part-3} The sum of $\series{\iota}_a$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$. Its Laplace transform along that ray is well-defined, and equal to $I_a$.
\end{enumerate}
\end{theorem}
\begin{todo}[In parallel with the ODE results, does this theorem help us accomplish something interesting or justify a point of view?]\end{todo}
%
\subsubsection{Other results}\label{sec:other_results}
%
\paragraph{New perspectives on the Laplace transform}
%
For Borel summation to work as described in Theorems~\ref{thm:soln_is_Borel_sum} and~\ref{thm:maxim}, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point. To explain this aspect of Borel regularity, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$. Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$. The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$. The details of this picture are discussed in Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}.
\begin{center}
\phaseSpaceLaplace
\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point. The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
\end{center}

@@

In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
 \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
%
\paragraph{Links to resurgence}
%
The examples we study all involve {\em resurgent functions} in the position domain. \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}. Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}. Conjecturally, this property extends to more general thimble integrals---perhaps even infinite-dimensional ones \cite[examples~5--6]{Maxim_slide_ERC}. The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave. \begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
%
\subsection{Organization of the paper}\label{sec:org}
%
\begin{revised}
In Section~\ref{sec:historical-context}, we contextualize our work by reviewing some classical results related to Borel regularity. These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.

In section~\ref{sec:Laplace-Borel-general}, we introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results. To make this section more self-contained, we review basic definitions and properties in Section~\ref{laplace:ordinary} and the beginnings of Sections \ref{sec:geometry_borel} and \ref{sec:borel-laplace-homom}.

@@

In Appendix~\ref{shifting}, we prove a fact about the relationship between integral and differential equations which is used in some of our examples.
\end{revised}
%
\begin{todo}\par [Consider going back to non-separated style.]\end{todo}\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles. This could help the reader to contextualize our results in the literature. Then, in Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform. The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{laplace:ordinary}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}. Then, Section~\ref{sec:proof_main_results} contains proofs of the main results. Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one. 
We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject. \begin{todo}[Appendix~\ref{shifting}?]\end{todo}
\end{draft}
%
\subsection{Notation}
In reasoning about Borel summation, it is important to keep track of whether we are working with holomorphic functions or formal series, and whether we are working on the position domain (the Borel plane) or the frequency domain (the $z$ plane). We have adopted a variable naming convention that makes these distinctions apparent at a glance.
\begin{notation*}
Functions and series on the frequency and position domains are named as follows.
\begin{center}
\begin{tabular}{c|c|c}
& \textbf{Analytic}: no tilde & \textbf{Formal}: tilde \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\phi$ & $\series{\phi}$ \\[1mm]
\end{tabular}
\end{center}
We will sometimes use a hat to emphasize that we got a holomorphic function $\hat{\phi}$ by taking the sum of formal series $\series{\phi}$.

@@

Here are some examples of this notation in action. Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the position domain into functions on the frequency domain, we might write $\laplace_{\zeta,0} \phi = \Phi$. On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
%
\begin{todo}Add the notation for integrals\end{todo}
\subsection{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

@@

The formal solutions of a level~$1$ ODE are always resurgent series~\cite[Proposition~2.2.1]{EcalleIII}. \'{E}calle proved this by using formal perturbation theory to solve a corresponding integral equation in the position domain. Using the ``formalism of singularities'' to understand how the singularities of the perturbative solution would propagate from one order of perturbation to the next, \'{E}calle showed that the pertrubation series would converge to an endlessly analytically continuable function. Loday-Richaud and Remy went on to show that this function always has a well-defined Laplace transform, so the corresponding formal solution in the frequency domain is Borel summable~\cite{loday-Remy2011}. Malgrange got similar results by working with differential equations, rather than integral equations, on the position domain~\cite{malgrange--fourier}.
%
\subsubsection{Solving Riemann--Hilbert problems}
%
\begin{revised}A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}. Local solutions of the ODE correspond to local flat sections of the connection. We can therefore use the theory of meromorphic connections to study level~$1$ ODEs. In particular, given an ODE, we can set up a Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE. \begin{todo}[Add reference]\end{todo}

To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the frame of solutions at $z = 0$ and $z = \infty$, and we also fix its discontinuities---the Stokes data prescribing how the frame jumps across each Stokes ray. A solution is then given by a piecewise analytic function which is holomorphic away from the Stokes rays and has the prescirbed asymptotics and discontinuities.\end{revised}

In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}. These cases include some Riemann--Hilbert problems arising from level~1 ODEs. For example, in Section~6.2.1 of \cite{kontsevich2022analyticity}, Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures. As mentioned in Section~\ref{borel-reg:explanatory-power}, every thimble integral satisfies some ODE. Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgent series.
\begin{todo}\par
Discuss examples where the Riemann--Hilbert problem corresponding to an ODE can be solved.
\begin{itemize}
\item Dubrovin
\item Kontsevich--Soibelman
\item Bridgeland
\item Gaiotto--Moore--Nietzke
\end{itemize}
\end{todo}
%
\subsubsection{Laplace transform methods and fixed point iteration}
%
All of the historical approaches we have discussed so far start by looking for formal solutions. In this paper, we will focus on a different kind of approach, where we start by looking for analytic solutions expressed as Laplace transforms. By carefully choosing the starting point of the Laplace transform, we get analytic solutions which are asymptotic to Poincar\'{e}'s formal ones. These solutions will turn out to be Borel regular.

@@

Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}. In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants. \begin{todo}[\textbf{V} Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}}

@@

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}\label{prop:inverse_laplace_analytic}
\begin{todo}[\textbf{A} Correct proof, and possibly remove constant]\end{todo} \begin{old}Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont},\end{old} \begin{revised}Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$,\end{revised} and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$. \begin{old}Choose any $\Lambda' > \Lambda$.\end{old} \begin{revised}Let $\Lambda' = \Lambda / \cos(\Theta)$.\end{revised} Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
\end{prop}
\begin{proof}
Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$. Choosing some $\Lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$. 
%
The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

%%\newcommand{\pathdis}{1.5625}
%%\newcommand{\pathoffset}{0.375}
\newcommand{\pathspread}{20}

@@

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick, black line is the path $\mathcal{C}$.}
\end{center}
Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. \begin{revised}Along $\mathcal{C}$, we have \begin{todo}[\textbf{A} where does the estimate come from?]\end{todo}
\[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
for some $\mu \in (\Lambda, \Lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big). \]
\begin{todo}[Why on $\mathcal{C}$ the real part of $z$ is bounded like that?]\end{todo}\end{revised}

@@

& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,

@@

[\textbf{V} add $\theta$] [\textbf{A} read through proof]

>>>>

Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.
\begin{theorem}[also \ref{thm:maxim-proof}]\label{thm:maxim}
If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly:
\begin{enumerate}
\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$. Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
\item\label{part-2} The Borel transform $\series{\iota}_a \defeq \borel_\zeta \series{I}_a$ converges near $\zeta = \alpha$.
\item\label{part-3} The sum of $\series{\iota}_a$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$. Its Laplace transform along that ray is well-defined, and equal to $I_a$.
\end{enumerate}
\end{theorem}
\begin{draft}
This result confirms the expectations that thimble integrals are equal to the Borel resummation of its asymptotics~\cite[Section~2]{dunne-unsal}. Although the same result is conjectured to hold in higher dimensions, our proof might not straighfowardly generalize, hence we leave the discussion to future works.

Notice also that an alternative proof can be done using Nevanlinna's theorem~\cite{nevanlinna}, but it will require an accurate control of the asymptotics of $I_a$, which should be uniform and 1-Gevrey in a large enough sector. Instead, our approach avoids the analysis of the asymptotics by working in the position domain. In fact, we use that $I_a$ can be regarded as a Laplace trasnform.  
\end{draft}
\begin{revised}
For one-dimensional thimbles, this result confirms the expectation that evaluating a thimble integral should be equivalent to taking the Borel sum of its asymptotic series~\cite[Section~2]{dunne-unsal}. Confirming this expectation in higher dimensions would be an interesting topic for future work, since our argument may not generalize straightforwardly.

As an alternative to our argument, Theorem~\ref{thm:maxim} could be deduced from Nevanlinna's theorem~\cite{nevanlinna}. However, that would require a careful asymptotic analysis of $I_a$: one would have to show that its asymptotic series is $1$-Gevrey and uniformly asymptotic to it on a large enough sector. We avoid this asymptotic analysis by working in the position domain and recasting $I_a$ as a Laplace transform integral.
\end{revised}
%
\subsubsection{Other results}\label{sec:other_results}
%
\paragraph{New perspectives on the Laplace transform}
%
For Borel summation to work as described in Theorems~\ref{thm:soln_is_Borel_sum} and~\ref{thm:maxim}, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point. To explain this aspect of Borel regularity, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$. Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$. The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$. The details of this picture are discussed in Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}.
\begin{center}
\phaseSpaceLaplace
\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point. The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
\end{center}

@@

In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
 \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
%
\paragraph{Links to resurgence}
%
The examples we study all involve {\em resurgent functions} in the position domain. \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}. Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}. Conjecturally, this property extends to more general thimble integrals---perhaps even infinite-dimensional ones \cite[examples~5--6]{Maxim_slide_ERC}. The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave. \begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
%
\subsection{Organization of the paper}\label{sec:org}
%
In Section~\ref{sec:historical-context}, we contextualize our work by reviewing some classical results related to Borel regularity. These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.

In Section~\ref{sec:Laplace-Borel-general}, we introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results. To make this section more self-contained, we review basic definitions and properties in Section~\ref{laplace:ordinary} and the beginnings of Sections \ref{sec:geometry_borel} and \ref{sec:borel-laplace-homom}.

@@

In Appendix~\ref{shifting}, we prove a fact about the relationship between integral and differential equations which is used in some of our examples.
%
\subsection{Notation}
In reasoning about Borel summation, it is important to keep track of whether we are working with holomorphic functions or formal series, and whether we are working on the position domain (the Borel plane) or the frequency domain (the $z$ plane). We have adopted a variable naming convention that makes these distinctions apparent at a glance.
\begin{notation*}
Functions and series on the frequency and position domains are named as follows.
\begin{center}
\begin{tabular}{c|c|c}
& \textbf{Analytic}: no tilde & \textbf{Formal}: tilde \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\phi$ & $\series{\phi}$ \\[1mm]
\end{tabular}
\end{center}
We will sometimes use a hat to emphasize that we got a holomorphic function $\hat{\phi}$ by taking the sum of formal series $\series{\phi}$.

@@

Here are some examples of this notation in action. Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the position domain into functions on the frequency domain, we might write $\laplace_{\zeta,0} \phi = \Phi$. On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
%
\begin{todo}[Add the notation for integrals. Reference regular singular Volterra paper, and also more or less copy its notation description.]\end{todo}
\subsection{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

@@

The formal solutions of a level~$1$ ODE are always resurgent series~\cite[Proposition~2.2.1]{EcalleIII}. \'{E}calle proved this by using formal perturbation theory to solve a corresponding integral equation in the position domain. Using the ``formalism of singularities'' to understand how the singularities of the perturbative solution would propagate from one order of perturbation to the next, \'{E}calle showed that the pertrubation series would converge to an endlessly analytically continuable function. Loday-Richaud and Remy went on to show that this function always has a well-defined Laplace transform, so the corresponding formal solution in the frequency domain is Borel summable~\cite{loday-Remy2011}. Malgrange got similar results by working with differential equations, rather than integral equations, on the position domain~\cite{malgrange--fourier}.
%
\subsubsection{Solving Riemann--Hilbert problems}
%
A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}. Local solutions of the ODE correspond to local flat sections of the connection. We can therefore use the theory of meromorphic connections to study level~$1$ ODEs. In particular, given an ODE, we can set up a Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.

To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the frame of solutions at $z = 0$ and $z = \infty$, and we also fix its discontinuities---the Stokes data prescribing how the frame jumps across each Stokes ray. A solution is then given by a piecewise analytic function which is holomorphic away from the Stokes rays and has the prescirbed asymptotics and discontinuities.

In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}. These cases include some Riemann--Hilbert problems arising from level~1 ODEs. For example, in Section~6.2.1 of \cite{kontsevich2022analyticity}, Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures. As mentioned in Section~\ref{borel-reg:explanatory-power}, every thimble integral satisfies some ODE. Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgent series.
%
\subsubsection{Laplace transform methods and fixed point iteration}
%
All of the historical approaches we have discussed so far start by looking for formal solutions. In this paper, we will focus on a different kind of approach, where we start by looking for analytic solutions expressed as Laplace transforms. By carefully choosing the starting point of the Laplace transform, we get analytic solutions which are asymptotic to Poincar\'{e}'s formal ones. These solutions will turn out to be Borel regular.

@@

Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}. In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as exponential period integrals \cite{deligne2007singularites,Maxim_lectures}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants. \begin{todo}[\textbf{V} Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}}

@@

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}\label{prop:inverse_laplace_analytic}
\begin{todo}[\textbf{A} Correct proof, and possibly remove constant] [\textbf{V} read it]\end{todo} \begin{old}Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont},\end{old} \begin{revised}Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$,\end{revised} and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$. \begin{old}Choose any $\Lambda' > \Lambda$.\end{old} \begin{revised}Let $\Lambda' = \Lambda / \cos(\Theta)$.\end{revised} Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
\end{prop}
\begin{proof}
\begin{revised}The boundary of $\widehat{\Omega}_\alpha^\Lambda$ consists of two rays connected by a circular arc. Extend the rays until they meet, forming the boundary of a sector with opening angle $\pi - \Theta$. Expand that sector by angle $\varepsilon/2$ on both sides. The edges of the expanded sector form a path $\mathcal{C}$ within $\widehat{\Omega}_\alpha^\Lambda$, as shown in Figure~\ref{fig:ref-path}.\end{revised}\begin{old}Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$. Choosing some $\Lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$. 
%
The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.\end{old}
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

%%\newcommand{\pathdis}{1.5625}
%%\newcommand{\pathoffset}{0.375}
\newcommand{\pathspread}{35}

@@

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick, black line is the path $\mathcal{C}$.}\label{fig:ref-path}
\end{center}
\begin{old}Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.\end{old} \begin{revised}The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon/2$. Parameterize it using the arc length parameter $t$ which is zero where the rays meet. Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,. \]
On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
\begin{todo}[Justify bound and add pictures.]\end{todo}\end{revised}

@@

& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \begin{revised}\big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\end{revised} \|\Phi\|_{\sigma, \Lambda}\,dt \\
& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \begin{revised}\big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\end{revised}\,dt,

@@

[\textbf{V} add $\theta$, or explain that it's missing, Fix proof] [\textbf{A} read through proof]
